This paper is based on a data set consisting of prices of the four cryptocurrencies of interest Bitcoin, Etherium, XRP and Litecoin, of the CMC Crypto 200 Index and of the ten year US treasury bond. The data was sourced form Yahoo! through its Application Programming Interface (API). For each of the above mentioned assets, the daily (adjusted) closing price was retrieved. The data set spans from January 1, 2018 to November 12, 2022. As the CMC Crypto 200 Index was launched only at year end 2018, there is a lack of data with respect to the index for the first year within our sample. 
\\
The final data set as well as the code that was needed to create it are openly accessible on GitHub and allow for reproduction of our exact results:


Here you can provide, if applicable, information about the dataset(s) whose creation, collection, management, access, processing or analysis have been discussed in this paper, following this schema:
\paragraph{Object name} Typically the name of the file or file set in the repository.
\paragraph{Format names and versions} E.g., ASCII, CSV, Autocad, EPS, JPEG, Excel, SQL, etc.
\paragraph{Creation dates} The start and end dates of when the data was created (YYYY-MM-DD).
\paragraph{Dataset creators} Please list anyone who helped to create the dataset (who may or may not be an author of the data paper), including their roles (using and affiliations).
\paragraph{Language} Languages used in the dataset (i.e., for variable names etc.).
\paragraph{License} The open license under which the data has been deposited (e.g., CC0). 
\paragraph{Repository name} The name of the repository to which the data is uploaded. E.g., Figshare, Dataverse, etc. 
\paragraph{Publication date} If already known, the date in which the dataset was published in the repository (YYYY-MM-DD).
